Prediction of the 2020 Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd

---
title: "Prediction of the 2020 Presidential Election"
subtitle: "Spoiler Alert: Trump Wins"
author: "Anees Shaikh, Jaffa Romain, Lu Mu, and Cameron Fryer"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | The purpose of this analysis is to forecast the results of the upcoming United States 2020 presidential election. In this paper, we first consider the Democracy Fund + UCLA Nationscape Wave 50 dataset, which contains the results of a survey (conducted June 25-July 1, 2020) on American voter attitudes. Thereafter, the survey data is used to train our model relating voter intent to 4 explanatory variables. The model is then applied to the post-stratification dataset; namely, the results of the 2018 1-year American Community Survey (ACS), to get predictions representative of the target population. Since the ACS data pertains to individual persons and their characteristics, the associated use of our model allows us to conclude that Donald Trump will be relected as the President of the United States, winning the popular vote by ___ with a margin of error of ______
Keywords: forecasting; US 2020 election; Trump; Biden; multilevel regression with post-stratification
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Prediction of the 2020 Presidential Election"
subtitle: "Spoiler Alert: Trump Wins"
author: "Anees Shaikh, Jaffa Romain, Lu Mu, and Cameron Fryer"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: The purpose of this analysis is to forecast the results of the upcoming United States 2020 presidential election. In this paper, we first consider the Democracy Fund + UCLA Nationscape Wave 50 dataset, which contains the results of a survey (conducted June 25-July 1, 2020) on American voter attitudes. Thereafter, the survey data is used to train our model relating voter intent to 4 explanatory variables. The model is then applied to the post-stratification dataset; namely, the results of the 2018 1-year American Community Survey (ACS), to get predictions representative of the target population. Since the ACS data pertains to individual persons and their characteristics, the associated use of our model allows us to conclude that Donald Trump will be relected as the President of the United States, winning the popular vote by ___ with a margin of error of ______
Keywords: forecasting; US 2020 election; Trump; Biden; multilevel regression with post-stratification
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---
